---
title: "Untitled"
author: "Lisa Reiber"
date: "3/15/2021"
output:
  html_document:
    keep_md: TRUE
theme: "flatly"
---

```{r setup, include=FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
pacman::p_load(tidyverse, janitor)

source("helper_functions.R")
# fs_codebook(c())
```

```{r}
language <- c("R", "R", "Python", "Julia", "SQL", NA)

fake_survey <- data.frame(Q2_MC_r = sample(c('Ja','Nicht Gew채hlt', NA), 500, rep = TRUE),
                          Q2_MC_python = sample(c('Ja','Nicht Gew채hlt', NA), 500, rep = TRUE), 
                          Q2_MC_julia = sample(c('Ja','Nicht Gew채hlt', NA), 500, rep = TRUE), 
                          Q2_MC_sql = sample(c('Ja','Nicht Gew채hlt', NA), 500, rep = TRUE), 
                          Q1_SC_fav_lang = sample(language, 500, rep = TRUE)
                          ) %>% 
  rownames_to_column(var = "id") %>% 
  mutate(id = as.numeric(id))

```

# Single Choice

Q1: What is your favourite language ?

## Janitor::tabyl

### short
```{r}
fake_survey %>% janitor::tabyl(Q1_SC_fav_lang) 
```

### fancy
```{r warning = FALSE}
fake_survey %>% 
  janitor::tabyl(Q1_SC_fav_lang, show_na = FALSE) %>% 
  arrange(desc(n)) %>% 
  janitor::adorn_pct_formatting() %>% 
  janitor::adorn_title(row_name = "Favourite Language", col_name = "")
```

## count & mutate

### short
```{r}
fake_survey %>% dplyr::count(Q1_SC_fav_lang) 
```

### fancy
```{r}
fake_survey %>% 
  drop_na(Q1_SC_fav_lang) %>% 
  count(`Favourite Language` = Q1_SC_fav_lang, name = "Frequency", sort = TRUE) %>% 
  mutate("Proportion" = round(Frequency / sum(Frequency) * 100, 1),
         "Prop in Percent" = paste0(Proportion, "%"))
```

we like it so we turn it into a function...

```{r}
fake_survey %>% gen_sc_table(type = "fancy")

# same as:
# fake_survey %>% 
#  gen_sc_table(sc_var = "Q1_SC_fav_lang", 
#               sc_label = "Favourite Language", 
#               type = "fancy")
```

# Multiple Choice

Q2: Which programming Languages do you know?

As we can see, there are multiple variables for question 2. For each language that participants were able to choose from, one variable was generated.

## R
```{r}
fake_survey %>% 
 gen_sc_table(sc_var = "Q2_MC_r", 
              sc_label = "Known Language: R", 
              type = "fancy")
```
## Python

```{r}
fake_survey %>% 
 gen_sc_table(sc_var = "Q2_MC_python", 
              sc_label = "Known Language: Python", 
              type = "fancy")
```

## How can we compare all of the answers?

### Step1: Select relevant data

How do we select all the relevant questions?

We can identify all questions of an item battery by their stem. And then we can use the tidyselect helpers `tidyselect::starts_with()`

```{r define mc-stem}
mc_stem_selected <- "Q2_MC_"
```

```{r}
mc_selected <- fake_survey %>% 
  select(id, starts_with(all_of(mc_stem_selected))) 
```

let's take a look
### Step2: Reshape to long format

How we 
```{r}
mc_long <- mc_selected %>% 
  pivot_longer(-id)
```
```{r}
mc_long %>% 
  janitor::tabyl(name, value)
```

How do I get frequencies?

```{r}
mc_long %>% 
  janitor::tabyl(name, value) %>% 
  adorn_percentages(denominator = "row") %>% 
  adorn_totals(where = "col") %>% 
  adorn_ns()
```

```{r}
mc_long %>%
  filter(value == "Ja") %>% 
  janitor::tabyl(name) %>% 
  adorn_pct_formatting() %>% 
  adorn_totals()
```

What if I want to know the Anteil of peopgle who selected a certain language? 

Your turn :)
```{r}

```


# cut outs
```{r}
fav_color <- c('Green', 'Red','Orange','Blue','Purple','Grey','Black','Yellow','White','Lavender')
```